\documentclass{beamer}

\usepackage{amsmath}
% \usepackage{dingbat}
\usepackage{twemojis}
\usepackage{xspace}

\input{../../papers/macros/style.tex}
\input{../../papers/macros/primitives.tex}

\usepackage{tikz}

\newcommand{\shrug}[1][]{%
\begin{tikzpicture}[baseline,x=0.8\ht\strutbox,y=0.8\ht\strutbox,line width=0.125ex,#1]
\def\arm{(-2.5,0.95) to (-2,0.95) (-1.9,1) to (-1.5,0) (-1.35,0) to (-0.8,0)};
\draw \arm;
\draw[xscale=-1] \arm;
\def\headpart{(0.6,0) arc[start angle=-40, end angle=40,x radius=0.6,y radius=0.8]};
\draw \headpart;
\draw[xscale=-1] \headpart;
\def\eye{(-0.075,0.15) .. controls (0.02,0) .. (0.075,-0.15)};
\draw[shift={(-0.3,0.8)}] \eye;
\draw[shift={(0,0.85)}] \eye;
% draw mouth
\draw (-0.1,0.2) to [out=15,in=-100] (0.4,0.95); 
\end{tikzpicture}}


\def\comring{\ensuremath{\mathsf{comring}}\xspace}
\def\compk{\ensuremath{\mathsf{compk}}\xspace}


\title{Polakdot / Machine elves}

\author{Jeffrey Burdges}
\date{20 June 2024}



\begin{document}

\maketitle



\begin{frame}

Ignore the stupid inefficencies in blockchains \\ \medskip
\hspace{10pt} Proof-of-work \\
\hspace{10pt} Irregular leader ellections in Praos \\
\hspace{10pt} Radix 16 hashing in ETH \\
\hspace{10pt} Bad VMs and scripting \\
\hspace{10pt} Memepools \\
\hspace{10pt} Not batch verifying \\

\pause\bigskip\bigskip

Ignore most harder inefficencies too \\ \medskip
\hspace{10pt} Mass replication \\
\hspace{10pt} Metered execution aka gas \\
\hspace{10pt} Single threaded execution \\
\hspace{10pt} Deterministic execution \\

\end{frame}



\begin{frame}

All of web2 requires ``sharding'' aka horizontal data partitioning \\ \medskip

\hspace{10pt} because services grow beyond what any one machine can do.

\pause\bigskip\bigskip\bigskip

Blockchains inherently simulate a single machine!

\pause\bigskip\bigskip\bigskip

Are blockchains only tools for costly services like finance?

\end{frame}



\begin{frame}

Idea:\  Cryptographic proof aka zk roll ups \\ \bigskip

All blocks have some succinct-ish cryptographic proof

\bigskip\bigskip

Advantage:  Weaker assumptions, but exactly what depends. \\ \smallskip

\bigskip\bigskip

Advantage:  Recursive in theory.  And composible. \\ \medskip

\hspace{10pt} Many shards in one block \\ \smallskip
\hspace{10pt} Verify ancestry ala Mina  \\

\bigskip\bigskip

Disadvantage: Interchain latency in hours

\end{frame}



\begin{frame}

``At present, zk roll up provers cost 1 to 100 million times the cost of a single verifier'' \\ \smallskip
- Justin Thaler (a16z)

\bigskip\bigskip

ETH pays almost 1 million nodes, so bandwidth effective there, \\ \medskip 

\hspace{10pt} But over paying one million fold !?! \\ \smallskip
\hspace{10pt} And elsewhere?

\pause\bigskip\bigskip

Actually worse given opertunity costs of decentralized provers.  \\ \medskip 

\hspace{10pt} And MEV becomes fatal here, but unavoidable.

\end{frame}



\begin{frame}

Idea:\  Concentration inequalities \\ \bigskip\bigskip

Assume 80\% honest plus perfect-ish randomness plus $\cdots$  \\ \medskip

Randomly assing 1000 validators to each shard \\ \medskip

Argue 2/3rd honest on each shard using Chebyshev/Hoeffding \\ \medskip

\hspace{5pt} Voila bridges become trustworthy 

\bigskip\bigskip

Advantage:  $1000 \ll 1,000,000$ but you pay bandwidth too.

\bigskip\bigskip

{\em OmniLedger: A Secure, Scale-Out, Decentralized Ledger via Sharding} by Bryan Ford's DEDIS group (EPFL)
% Eleftherios Kokoris-Kogias, Philipp Jovanovic, Linus Gasser†, Nicolas Gailly†, Ewa Syta, Bryan Ford

\end{frame}



\begin{frame}

Idea:\  Concentration inequalities \\ \bigskip\bigskip

Advantage:  Interchain latency in seconds or minutes, post-finality \\ \bigskip\bigskip

Disadvantage: Non-recursive \\ \bigskip\bigskip

\pause

Pseudo-disadvantage: Nobody bothers \\ \medskip

\hspace{5pt} Awful lot of professor coins mess up shard sizes, but.. 

\end{frame}


\begin{frame}

Tool:  Availability commitment via erasure coding \\ \bigskip

Who does provides? \quad  Who samples? \\ \bigskip\medskip

Rateless codes -- Attacker merely solves HP hard problem \\
\hspace{5pt}  Otherwise very fast \& very cool \\ \bigskip

2d Reed-Solomn -- Attacker must hide 1/4th \\ \smallskip
\hspace{5pt}  Allows partial reconstruction for $O(\sqrt{n})$ sized fraud proofs \\ \smallskip
\hspace{5pt}  Off-chain \& you lots, or you $+$ \shrug \quad bandwidth?!? \\ \bigskip

1d Reed-Solomn -- Attacker must hide 2/3rds \\ \smallskip
\hspace{5pt}  Assume 2/3rd honest, so validators \& validators. \\ \smallskip
\hspace{5pt}  All or nothing reconstruction, but allows batch verification 

\end{frame}



\begin{frame}

Idea:\  Optimistic roll ups \\ \bigskip\bigskip

1. 2d Reed-Solomn availability \\ \medskip

2. Erasure code blocks so someone could check them \\ \medskip

3. Some randos magically appear and check \\ \smallskip

\hspace{10pt} Why do they check?  \shrug \\ \medskip

4. Attempt recovery if cheated \\ \bigskip\bigskip

Disadvantage:  Interchain latency of a week 

\end{frame}



\begin{frame}

Idea: Byzantine ``cut n choose'' proof \\ \bigskip\bigskip

Assume 2/3rd honest plus synchrony$\dag$ \\ \bigskip

0. Make blocks state-less \\ \medskip

1. At least one validator ``backs'' the block \\ \medskip

2. Wait upon availability by 1d Reed-Solomn \\ \medskip

3. Interchain messages sent optimistically \\ \medskip

4. Validators self-assign using ELVES approval gadget \\ \medskip

5. Revert chain if approval gadget rejects \\ \medskip

6. Finality waits upon approval gadget \\ \medskip

\end{frame}



\begin{frame}

Advantage:  Interchain latency of seconds, even pre-finality \\ \bigskip

Advantage:  35-ish checkes, 29x cheaper than OmniLedger \\ \smallskip
\hspace{10pt} 15 may be possible!

\pause\bigskip\bigskip

Disadvantage:  Complexity \\ \bigskip

Disadvantage:  Soundness assumes 2/3rd honest plus synchrony$\dag$ \\ \bigskip

Disadvantage:  Gossip is $O(n^2)$ bandwidth, \\ \smallskip
\hspace{10pt} but 1000 works, so composes with OmniLedger \\ \bigskip

\end{frame}



\begin{frame}

ELVES approval gadget: \\ \bigskip\bigskip

Escalate to everyone if anyone disputes. \\ \medskip

Tranche $t=0$.  Announce if core is $c_i$ for some $i$ where \\ \smallskip
\hspace{10pt}  $(c_1,\ldots,c_k) \leftarrow \mathsf{VRF}(r) \bmod \mathtt{num\_cores}$ \\ \medskip

Tranche $t>0$.  Announce if $t > t_c$ where \\ \smallskip
\hspace{10pt}  $\mathtt{t_c} \leftarrow \mathsf{VRF}(r \doubleplus c) \bmod \mathtt{max\_delay}$  \\ \medskip

Require enough tranche for 35 assignees, plus \\ \smallskip
\hspace{5pt} one extra tranche for each assignee who ``no shows'' \\ \medskip

\end{frame}





\end{document}


